% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{João Eduardo Montandon}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {software engineering, professor, researcher},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://ufmg.br/}{Universidade Federal de Minas Gerais} \\
  Colégio Técnico \\
  Antonio Carlos Avenue, 6627 \\
  Belo Horizonte, MG 31270-901 -- Brazil
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & +55 (31) 3409-7519 \\
    Email: & \href{mailto:jemaf@ufmg.br}{\tt jemaf@ufmg.br} \\
    Homepage: & \href{http://jemaf.github.io/}{\tt http://jemaf.github.io/} \\
  \end{tabular}
\end{minipage}


\section*{Education}
\begin{itemize}
  \item PhD in Computer Science, Universidade Federal de Minas Gerais (2020 -- Expected). \\
  \textbf{Thesis} Predicting Software Developers Technical Skills. \\
  \textbf{Advisor} Prof. Marco Tulio Valente.
  \item MSc in Computer Science, Universidade Federal de Minas Gerais (2013). \\
  \textbf{Dissertation} Documenting Application Programming Interfaces with Source Code Examples. \\
  \textbf{Advisor} Prof. Marco Tulio Valente.
  \item BS in Computer Science, Pontifícia Universidade Católica de Minas Gerais (2010).
\end{itemize}


\section*{Professional}
\begin{itemize}
\item Universidade Federal de Minas Gerais (2014 -- Now). \\
\textbf{Professor} at Colégio Técnico, where I lecture basic programming, web and mobile development classes. 
\item Pontomobi Informática (2014 -- 2014). \\
\textbf{Mobile Software Engineer} focused on iOS application development.
\item Faculdade COTEMIG (2013 -- 2014). \\
\textbf{Professor} at COTEMIG College, where I lecture basic programming and web development classes.
\item Avenue Code LLC (2013 -- 2014). \\
\textbf{Backend Software Engineer} working mainly with web technologies, focused on Java and Ruby. 
\end{itemize}


\section*{Publications {\footnotesize (international venues)}}

\subsection*{Journal Articles}
\begin{itemize}
\item Static Correspondence and Correlation between Field Defects and Warnings Reported by a Bug Finding Tool, 2012, {\it Software Quality Journal}, Springer, 241--257.
\item Study on the Relevance of the Warnings Reported by Java Bug-Finding Tools, 2011, {\it IET Software}, IET, 366--374.
\end{itemize}

\subsection*{Proceedings}

\begin{itemize}
\item Identifying Experts on Software Libraries and Frameworks among GitHub Users, in \textit{16th International Conference on Mining Software Repositories (MSR)}, 2019, 1--12 (to appear).
\item Documenting APIs with Examples: Lessons Learned with the APIMiner Platform, in \textit{20th Working Conference on Reverse Engineering (WCRE)}, 2013, 1--8.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
